---
title: "Health care access"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
runtime: shiny
resource_files:
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.cpg
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.dbf
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.prj
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.sbn
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.sbx
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.shp.xml
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.shx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(sf)
library(ggrepel)
library(scales)
library(shiny)
library(shinycssloaders)
library(ggiraph)
library(kableExtra)
library(rmapshaper)
library(cowplot)
library(DT)
```

```{r loading jon docs and shapefiles, cache=TRUE, include=FALSE}
theme_bar <- theme_bw() +
  theme(panel.grid.major = element_line(color = "grey70", size = 0.1),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_text(face = "bold"),
        panel.border = element_blank(),
        legend.background = element_rect(fill = "transparent", color = "transparent"),
        legend.key = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

theme_line <- theme_bw() +
  theme(legend.background = element_rect(fill = "transparent", color = "transparent"),
        legend.key = element_rect(fill = "transparent"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(color = "grey70", size = 0.1),
        axis.ticks = element_blank(),
        axis.text = element_text(face = "bold"),
        panel.border = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

theme_sf <- theme_bw() +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "white"),
        panel.border = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

counties.regions <- read_csv("Data/Join docs/county_regions.csv") %>%
  mutate(countyfp = formatC(countyfp, width = 3, flag = "0"),
         Name = str_to_title(Name),
         Name = str_replace(Name, "Q", "q"),
         Name = str_replace(Name, "Of The", "of the"),
         Dem_Desc = ifelse(Name == "Minnesota", "Minnesota", Dem_Desc),
         Name = str_replace(Name, "Mcleod", "McLeod"),
         planning.region = str_replace(planning.region, " Minnesota", ""),
         edr = str_replace(edr, "  ", " "))

edr.pr <- counties.regions %>%
  distinct(edr, .keep_all = TRUE) %>%
  select(5,6) %>%
  mutate(edr = str_replace(edr, "  ", " "),
         planning.region = str_replace(planning.region, " Minnesota", ""))

color.ruca <- c("Entirely rural" = "#5CA81F", "Town/rural mix" = "#C7EF99", "Urban/town/rural mix" = "#d8b365", "Entirely urban" = "#a6611a", "Minnesota" = "black")

color.pr <- c("Northwest" = "#810f7c","Northeast" = "#fe9929", "Central" = "#076324", "Seven County Mpls-St Paul" = "#d8b365", "Southwest" = "#1f78b4", "Southeast" = "#d7301f", "Minnesota" = "black")

color.edr <- c("EDR 1 - Northwest" = "#b3cde3", "EDR 2 - Headwaters" = "#8c96c6", "EDR 3 - Arrowhead" = "#fe9929", "EDR 4 - West Central" = "#8856a7", "EDR 5 - North Central" = "#810f7c", "EDR 6E- Southwest Central" = "#e5f5f9", "EDR 6W- Upper Minnesota Valley" = "#bdc9e1", "EDR 7E- East Central" = "#99d8c9", "EDR 7W- Central" = "#2ca25f", "EDR 8 - Southwest" = "#74a9cf", "EDR 9 - South Central" = "#0570b0", "EDR 10 - Southeast" = "#d7301f", "EDR 11 - 7 County Twin Cities" = "#d8b365", "Minnesota" = "black")

color.counties <- scale_color_brewer(palette = "Dark2",
                       guide = guide_legend(ncol = 3))

mn_counties <- st_read("Data/Shapefiles/county shapefiles/MNCounties_MNDOT.shp", quiet = TRUE) %>%
  ms_simplify(keep = .01, keep_shapes = TRUE)
```

```{r master objects, include = FALSE, cache=TRUE}
master.ip.distances.ruca <- read_csv("Data/Access/Master-ip-distances-ruca.csv") %>%
  mutate(Dem_Desc = fct_relevel(Dem_Desc, "Entirely rural", "Town/rural mix", "Urban/town/rural mix", "Entirely urban"))

master.ip.distances.pr <- read_csv("Data/Access/Master-ip-distances-pr.csv") %>%
  mutate(planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"))

master.ip.distances.edr <- read_csv("Data/Access/Master-ip-distances-edr.csv") %>%
  mutate(planning.region = str_replace(planning.region, " Minnesota", ""),
         planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"),
         edr = fct_relevel(edr, "EDR 1 - Northwest", "EDR 2 - Headwaters", "EDR 3 - Arrowhead", "EDR 4 - West Central", "EDR 5 - North Central", "EDR 6E- Southwest Central", "EDR 6W- Upper Minnesota Valley", "EDR 7E- East Central", "EDR 7W- Central", "EDR 8 - Southwest", "EDR 9 - South Central", "EDR 10 - Southeast", "EDR 11 - 7 County Twin Cities", "Minnesota"))

master.op.distances.ruca <- read_csv("Data/Access/Master-op-distances-ruca.csv") %>%
  mutate(Dem_Desc = fct_relevel(Dem_Desc, "Entirely rural", "Town/rural mix", "Urban/town/rural mix", "Entirely urban"))

master.op.distances.pr <- read_csv("Data/Access/Master-op-distances-pr.csv") %>%
  mutate(planning.region = str_replace(planning.region, " Minnesota", ""),
         planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"))

master.op.distances.edr <- read_csv("Data/Access/Master-op-distances-edr.csv") %>%
  mutate(planning.region = str_replace(planning.region, " Minnesota", ""),
         planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"),
         edr = fct_relevel(edr, "EDR 1 - Northwest", "EDR 2 - Headwaters", "EDR 3 - Arrowhead", "EDR 4 - West Central", "EDR 5 - North Central", "EDR 6E- Southwest Central", "EDR 6W- Upper Minnesota Valley", "EDR 7E- East Central", "EDR 7W- Central", "EDR 8 - Southwest", "EDR 9 - South Central", "EDR 10 - Southeast", "EDR 11 - 7 County Twin Cities", "Minnesota"))

```

<br>

# Distances traveled by inpatient care and region {.tabset}

The rural-ness from which a patient originates has a significant impact on how likely they travel for the three inpatient services. In fact, patients from our most rural parts of the state traveled 3 to 4 times longer than their more urban colleagues. 

For example, patients from entirely rural areas traveled 77 miles for cardiology, where as patients from entirely urban counties averaged 21.

There were also significant regional differences. Broken down by planning regions, patient travel distances were significantly higher from other regions depending on the "rural-ness" of that planning region. The northern part of the state in particular had significantly higher travel times.

<br>

## RUCA

As a hospital becomes more rural, the distance their patients travel for a service becomes significantly longer. In fact, for the three analyzed services provided below, distances traveled for services by our most rural patients was 3 to 4 times more than our most urban patients. The largest difference was for neurology, where patients in entirely rural areas traveled 100 miles on average compared to just 22 for our entirely urban patients.

Another worrisome trend is that the distances traveled by our more rural patients has been increasing. For example, our more rural patients of the state traveled 60 miles on average in 2010, which increased to nearly 80 miles by 2018. This is an increase of 33%.

<br>

```{r charts distance traveled inpatient ruca}
ip.ruca.plot <- ggplot(master.ip.distances.ruca, aes(Year, mean.miles, color = Dem_Desc)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(Dem_Desc, "\nYear: ", Year, "\nService: ", service.line, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~service.line, ncol = 2, scales = "free_y") +
  labs(x="", y = "", color="", title = "Average miles traveled for inpatient service")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.ruca,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = ip.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))

```

## Planning Region

All regions outside of the seven county metro have higher travel distances to these services. The northern parts of the state were consistently the top two highest travel distances for these services. In addition, the Northwest, Northeast, and Southwest regions all had increasing travel times since 2010. 

<br>

```{r charts distance traveled inpatient pr}
ip.pr.plot <- ggplot(master.ip.distances.pr, aes(Year, mean.miles, color = planning.region)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(planning.region, "\nYear: ", Year, "\nService: ", service.line, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~service.line, ncol = 2, scales = "free_y") +
  labs(x="", y = "", color="", title = "Average miles traveled for inpatient service")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.pr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = ip.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

## EDR {.tabset}

Not surprisingly, there is plenty of variation within planning regions. Patients from EDRs that lack a significant economic center were likely to have higher travel distances. 

<br>

### Cardiology

<br>

```{r charts distance traveled inpatient cargiology edr, fig.height=9}
ip.card.edr.plot <- ggplot(filter(master.ip.distances.edr, service.line == "Cardiology"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(edr, "\nYear: ", Year, "\nService: ", service.line, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for inpatient service - cardiology")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = ip.card.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

### Neurology

<br>

```{r charts distance traveled inpatient neurology edr, fig.height=9}
ip.neur.edr.plot <- ggplot(filter(master.ip.distances.edr, service.line == "Neurology"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(planning.region, "\nYear: ", Year, "\nService: ", service.line, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for inpatient service - neurology")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = ip.neur.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

### Obstetrics

<br>

```{r charts distance traveled inpatient obstetrics edr, fig.height=9}

ip.obs.edr.plot <- ggplot(filter(master.ip.distances.edr, service.line == "Obstetrics"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(planning.region, "\nYear: ", Year, "\nService: ", service.line, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for inpatient service - obstetrics")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = ip.obs.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

<br>

# Distances traveled by outpatient care and region {.tabset}

Again, as a patient originates from a more rural area, the travel distances increase. However, these differences aren't as severe compared to inpatient services. Typically, the difference is double rather than 3 to 4 times longer.

<br>

## RUCA

Again, as a patient originates from a more rural area, the travel distances increase. However, the differences between the highest and lowest times are not as severe. It's about 1 to 1.5 times further. The most concerning is Stroke, where entirely rural patients traveled 35 miles, compared to 11 for entirely urban patients.

In addition, we are not seeing large increases in travel times compared to inpatient care. However, Diabetes is increasing for entirely rural patients for some reason.

<br>

```{r charts distance traveled outpatient ruca, fig.height=7}
op.ruca.plot <- ggplot(master.op.distances.ruca, aes(Year, mean.miles, color = Dem_Desc)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(Dem_Desc, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~type, ncol = 2, scales = "free_y") +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.ruca,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.ruca.plot, width_svg = 8, height_svg = 7) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))

```

## Planning Region

When broken down by regions, we are not seeing as large of differences. Of course, regions outside of the seven metro have longer travel distances, but typically less than double. Stroke is still kind of high as well as pneumonia.

<br>

```{r charts distance traveled outpatient pr, fig.height=8}
op.pr.plot <- ggplot(master.op.distances.pr, aes(Year, mean.miles, color = planning.region)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(planning.region, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~type, ncol = 2, scales = "free_y") +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.pr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.pr.plot, width_svg = 8, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))

```

## EDR {.tabset}

You still see plenty of differences within planning regions. Patients from our more rural EDRs have a significantly higher travel distance compared to other EDRs that may have more of an urban center in it. This is particularly true in Northwest and Southwest.

<br>

### COPD and Bronch

<br>

```{r charts distance traveled outpatient COPD and Bronch edr, fig.height=9}
op.bronch.edr.plot <- ggplot(filter(master.op.distances.edr, type == "COPD and Bronch"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(edr, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service - COPD and Bronch")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.bronch.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

### Diabetes

<br>

```{r charts distance traveled outpatient Diabetes edr, fig.height=9}
op.diab.edr.plot <- ggplot(filter(master.op.distances.edr, type == "Diabetes"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(edr, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service - Diabetes")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.diab.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

### Intracranial injury

<br>

```{r charts distance traveled outpatient intracranial edr, fig.height=9}
op.cran.edr.plot <- ggplot(filter(master.op.distances.edr, type == "Intracranial injury"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(edr, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service - Intracranial injury")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.cran.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

### Pneumonia

<br>

```{r charts distance traveled outpatient pneumonia edr, fig.height=9}
op.pneu.edr.plot <- ggplot(filter(master.op.distances.edr, type == "Pneumonia"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(edr, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service - Pneumonia")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.pneu.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```

### Stroke

<br>

```{r charts distance traveled outpatient stroke edr, fig.height=9}
op.stroke.edr.plot <- ggplot(filter(master.op.distances.edr, type == "Stroke"), aes(Year, mean.miles, color = edr)) +
  geom_smooth(se = FALSE, size = 2) +
  geom_point_interactive(size = 3, aes(data_id = Year, tooltip = paste(edr, "\nYear: ", Year, "\nService: ", type, "\nAverage miles traveled: ", comma(mean.miles), "\nMedian miles traveled: ", comma(median.miles), sep = ""))) +
  facet_wrap(~planning.region, ncol = 2) +
  labs(x="", y = "", color="", title = "Average miles traveled for outpatient service - Stroke")+
  scale_y_continuous(labels=scales::comma)+
  scale_x_continuous(breaks = seq(1900, 2050, 2)) +
  theme_line+
  scale_color_manual(values= color.edr,
                     guide = guide_legend(ncol = 3)) +
  theme(legend.position = "bottom")

girafe(ggobj = op.stroke.edr.plot, height_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))
```



