---
title: "Margins"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
runtime: shiny
resource_files:
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.cpg
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.dbf
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.prj
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.sbn
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.sbx
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.shp.xml
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.shx
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(sf)
library(ggrepel)
library(scales)
library(shiny)
library(shinycssloaders)
library(ggiraph)
library(kableExtra)
library(rmapshaper)
library(cowplot)
library(DT)
```

```{r loading jon docs and shapefiles, cache=TRUE, include=FALSE}
theme_bar <- theme_bw() +
  theme(panel.grid.major = element_line(color = "grey70", size = 0.1),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_text(face = "bold"),
        panel.border = element_blank(),
        legend.background = element_rect(fill = "transparent", color = "transparent"),
        legend.key = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

theme_line <- theme_bw() +
  theme(legend.background = element_rect(fill = "transparent", color = "transparent"),
        legend.key = element_rect(fill = "transparent"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(color = "grey70", size = 0.1),
        axis.ticks = element_blank(),
        axis.text = element_text(face = "bold"),
        panel.border = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

theme_sf <- theme_bw() +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "white"),
        panel.border = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

counties.regions <- read_csv("Data/Join docs/county_regions.csv") %>%
  mutate(countyfp = formatC(countyfp, width = 3, flag = "0"),
         Name = str_to_title(Name),
         Name = str_replace(Name, "Q", "q"),
         Name = str_replace(Name, "Of The", "of the"),
         Dem_Desc = ifelse(Name == "Minnesota", "Minnesota", Dem_Desc),
         Name = str_replace(Name, "Mcleod", "McLeod"),
         planning.region = str_replace(planning.region, " Minnesota", ""),
         edr = str_replace(edr, "  ", " "))

edr.pr <- counties.regions %>%
  distinct(edr, .keep_all = TRUE) %>%
  select(5,6) %>%
  mutate(edr = str_replace(edr, "  ", " "),
         planning.region = str_replace(planning.region, " Minnesota", ""))

color.ruca <- c("Entirely rural" = "#5CA81F", "Town/rural mix" = "#C7EF99", "Urban/town/rural mix" = "#d8b365", "Entirely urban" = "#a6611a", "Minnesota" = "black")

color.pr <- c("Northwest" = "#810f7c","Northeast" = "#fe9929", "Central" = "#076324", "Seven County Mpls-St Paul" = "#d8b365", "Southwest" = "#1f78b4", "Southeast" = "#d7301f", "Minnesota" = "black")

color.edr <- c("EDR 1 - Northwest" = "#b3cde3", "EDR 2 - Headwaters" = "#8c96c6", "EDR 3 - Arrowhead" = "#fe9929", "EDR 4 - West Central" = "#8856a7", "EDR 5 - North Central" = "#810f7c", "EDR 6E- Southwest Central" = "#e5f5f9", "EDR 6W- Upper Minnesota Valley" = "#bdc9e1", "EDR 7E- East Central" = "#99d8c9", "EDR 7W- Central" = "#2ca25f", "EDR 8 - Southwest" = "#74a9cf", "EDR 9 - South Central" = "#0570b0", "EDR 10 - Southeast" = "#d7301f", "EDR 11 - 7 County Twin Cities" = "#d8b365", "Minnesota" = "black")

color.counties <- scale_color_brewer(palette = "Dark2",
                       guide = guide_legend(ncol = 3))

mn_counties <- st_read("Data/Shapefiles/county shapefiles/MNCounties_MNDOT.shp", quiet = TRUE) %>%
  ms_simplify(keep = .01, keep_shapes = TRUE)
```

```{r prep master file, include=FALSE}
master.har <- read_csv("Data/HAR/Master-har.csv") %>%
  rename(year = rpt_year) %>%
  mutate(planning.region = str_replace(planning.region, " Minnesota", ""),
         edr = str_replace(edr, "  ", " ")) %>%
  rename(`Hospital Name` = 5)

```

# Margins of all hospitals

Below is a list of each hospital's 2018 total revenue, net income/loss, and their margin. 

<br>

```{r prep 2018 margin table for each hospital, include = FALSE}
har.margin.2018.table <- master.har %>%
  filter(code %in% c(250, 200),
         year == 2018) %>%
  mutate(code = ifelse(code == 200, "net.income", "total.revenue"),
         value = as.numeric(value),
         CAH = ifelse(CAH == "No", "Non-CAH", "CAH")) %>%
  spread(key = code, value = value) %>% 
  select(3,4,5,6,7,8,10,11,13,12, 14) %>%
  mutate(Margins = net.income/total.revenue)
  
```

```{r table of 2017 margins for each hospital}
datatable(har.margin.2018.table, class = "cell-border stripe", filter = "top", rownames = FALSE,
          options = list(scrollX = TRUE)) %>%
  formatStyle("Margins",
              target = "row",
              backgroundColor = styleInterval(c(-1, 0), c("red", "red", "transparent"))) %>%
  formatCurrency(7:8, "$") %>%
  formatPercentage(9)

```

<br>

# Analysis of margins of all hospitals by regions

Since 4% is considered a healthy margin for a hospital, it's important to see how many hospitals fall below that value.

<br>

## 2018 margins {.tabset}

Not suprisingly, given the number of hospitals that recorded a net loss in Southwest Minnesota for 2018, that region also has the highest number and percentage of hospitals that fall below the 4% margin threshold. Northeast also has a significanlty high number of hospitals below the threshold.

Even more telling is the RUCA chart. This psoitively shows that hospitals operating outside of our most urban counties are significantly more likely to have margins below the 4% threshold. Nearly 70% of the hospitals in entirely rural areas are below the threshold, while nearly half of the hospitals are below the threshold in the other non-entirely urban counties.

<br>

```{r prep margins for each hospital, include = FALSE}
har.margins <- master.har %>%
  filter(code %in% c(200, 250)) %>%
  mutate(code = ifelse(code == 200, "income.loss", "total.revenue"),
         value = as.numeric(value),
         CAH = ifelse(CAH == "No", "Non-CAH", "CAH")) %>%
  spread(key = code, value = value) %>%
  mutate(margins = income.loss / total.revenue,
         `Hospital Name` = str_replace(`Hospital Name`, "'", ""),
         planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"),
         Dem_Desc = fct_relevel(Dem_Desc, "Entirely rural", "Town/rural mix", "Urban/town/rural mix", "Entirely urban"))

har.margins.threshold.pr <- har.margins %>%
  mutate(below.threshold = ifelse(margins < .04, 1, 0)) %>%
  group_by(planning.region, year) %>%
  summarise(below.threshold = sum(below.threshold, na.rm = TRUE),
            total.n = n()) %>%
  ungroup() %>%
  mutate(pct.below.threshold = below.threshold / total.n)

har.margins.threshold.ruca <- har.margins %>%
  mutate(below.threshold = ifelse(margins < .04, 1, 0)) %>%
  group_by(Dem_Desc, year) %>%
  summarise(below.threshold = sum(below.threshold, na.rm = TRUE),
            total.n = n()) %>%
  ungroup() %>%
  mutate(pct.below.threshold = below.threshold / total.n)
  
```

```{r prep average margins, include = FALSE}
har.margins.avg.pr <- har.margins %>%
  group_by(year, planning.region) %>%
  summarise(avg.margins = mean(margins, na.rm = TRUE)) %>%
  ungroup()

har.margins.avg.ruca <- har.margins %>%
  group_by(year, Dem_Desc) %>%
  summarise(avg.margins = mean(margins, na.rm = TRUE)) %>%
  ungroup()
```

### Planning Region

<br>

```{r chart margins points pr}

har.margins.pr.plot <- ggplot(filter(har.margins, year == 2018), aes(planning.region, margins, color = planning.region)) +
        geom_point_interactive(size = 3, aes(data_id = margins, tooltip = paste(planning.region, "\nHospital Name: ", `Hospital Name`, "\nType of hospital: ", CAH, "\nTotal revenue: ", dollar(total.revenue), "\nNet income: ", dollar(income.loss), "\nMargin: ", percent(margins), sep = ""))) +
          geom_label(data = filter(har.margins.threshold.pr, year == 2018), size = 3, show.legend = FALSE, aes(x = planning.region, y = -.3, label = paste(below.threshold, " hospitals\nunhealthy margins\n", percent(pct.below.threshold), " of hospitals", sep = ""))) +
          geom_label(data = filter(har.margins.avg.pr, year == 2018), aes(x = planning.region, y = .4, label = paste("Avg margins\n", percent(avg.margins), sep = "")), size = 3, show.legend = FALSE) +
          geom_hline(yintercept = 0.04, color = "black") +
        labs(x="", y = "", color="", title = "Margins for each hospital in 2018")+
        scale_y_continuous(labels=scales::percent,
                           limits = c(-.4, .45))+
        theme_line+
        scale_color_manual(values= color.pr,
                           guide = guide_legend(ncol = 3)) +
        theme(legend.position = "bottom",
              axis.text.x = element_text(angle = 45, hjust = .9))
        
girafe( ggobj = har.margins.pr.plot, width_svg = 8, height_svg = 6) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE),
                 opts_zoom(max = 3))


```

### RUCA

<br>

```{r chart margins points ruca}
har.margins.ruca.plot <- ggplot(filter(har.margins, year == 2018), aes(Dem_Desc, margins, color = Dem_Desc)) +
        geom_point_interactive(size = 3, aes(data_id = margins, tooltip = paste(Dem_Desc, "\nHospital Name: ", `Hospital Name`, "\nType of hospital: ", CAH, "\nTotal revenue: ", dollar(total.revenue), "\nNet income: ", dollar(income.loss), "\nMargin: ", percent(margins), sep = ""))) +
          geom_label(data = filter(har.margins.threshold.ruca, year == 2018), size = 3, show.legend = FALSE, aes(x = Dem_Desc, y = -.3, label = paste(below.threshold, " hospitals\nunhealthy margins\n", percent(pct.below.threshold), " of hospitals", sep = ""))) +
          geom_label(data = filter(har.margins.avg.ruca, year == 2018), aes(x = Dem_Desc, y = .4, label = paste("Avg margins\n", percent(avg.margins), sep = "")), size = 3, show.legend = FALSE) +
          geom_hline(yintercept = 0.04, color = "black") +
        labs(x="", y = "", color="", title = "Margins for each hospital in 2018")+
        scale_y_continuous(labels=scales::percent,
                           limits = c(-.4, .5))+
        theme_line+
        scale_color_manual(values= color.ruca,
                           guide = guide_legend(ncol = 3)) +
        theme(legend.position = "bottom")
        
girafe( ggobj = har.margins.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE),
                 opts_zoom(max = 3))
```

<br>

## Percent of hospitals with margins below 4% {.tabset}

Now it's worth seeing if the number of hospitals experiencing these low margins are typical on any given year.

For the most part, the percentage of hospitals that have margins below 4% is staying relatively consistent. The Seven County metro has experienced a slight uptick while the Northwest has had a significant decrease in their percentage.

The RUCA chart shows that entirely urban counties have experienced a slight uptick while the entirely rural counties have experienced a slight down tick in their percentage. 

<br>

```{r prep margin trends, include = FALSE}
har.margins.trend.pr <- har.margins %>%
  mutate(below.threshold = ifelse(margins < .04, 1, 0)) %>%
  group_by(planning.region, year) %>%
  summarise(below.threshold.n = sum(below.threshold, na.rm = TRUE),
            total.n = n()) %>%
  ungroup() %>%
  mutate(pct.below.threshold = below.threshold.n / total.n)

har.margins.trend.ruca <- har.margins %>%
  mutate(below.threshold = ifelse(margins < .04, 1, 0)) %>%
  group_by(Dem_Desc, year) %>%
  summarise(below.threshold.n = sum(below.threshold, na.rm = TRUE),
            total.n = n()) %>%
  ungroup() %>%
  mutate(pct.below.threshold = below.threshold.n / total.n)

```

### Planning Region

<br>

```{r chart har margin trends pr}

har.margins.trend.pr.plot <- ggplot(har.margins.trend.pr, aes(year, pct.below.threshold, color = planning.region)) +
        geom_line(size = 2) +
        geom_point_interactive(size = 3, aes(data_id = pct.below.threshold, tooltip = paste(planning.region, "\nYear: ", year, "\nNumber of hospitals: ", total.n, "\nNumber with margins below 4%: ", below.threshold.n, "\nPercent of hospitals below threshold: ", percent(pct.below.threshold), sep = ""))) +
        labs(x="", y = "", color="", title = "Percent of hospitals with margins below 4%")+
        scale_y_continuous(labels=scales::percent)+
        scale_x_continuous(breaks = seq(1900, 2050, 2)) +
        theme_line+
        scale_color_manual(values= color.pr,
                           guide = guide_legend(ncol = 3)) +
        theme(legend.position = "bottom")
        
girafe( ggobj = har.margins.trend.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))


```

### RUCA

<br>

```{r charts har margin trends ruca}

har.margins.trend.ruca.plot <- ggplot(har.margins.trend.ruca, aes(year, pct.below.threshold, color = Dem_Desc)) +
        geom_line(size = 2) +
        geom_point_interactive(size = 3, aes(data_id = pct.below.threshold, tooltip = paste(Dem_Desc, "\nYear: ", year, "\nNumber of hospitals: ", total.n, "\nNumber with margins below 4%: ", below.threshold.n, "\nPercent of hospitals below threshold: ", percent(pct.below.threshold), sep = ""))) +
        labs(x="", y = "", color="", title = "Percent of hospitals with margins below 4%")+
        scale_y_continuous(labels=scales::percent)+
        scale_x_continuous(breaks = seq(1900, 2050, 2)) +
        theme_line+
        scale_color_manual(values= color.ruca,
                           guide = guide_legend(ncol = 3)) +
        theme(legend.position = "bottom")
        
girafe( ggobj = har.margins.trend.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))

```

<br>

# Analysis of margins of CAH hospitals by regions

This section examines whether there are any differences in margins between CAH and regular hospitals.

<br>

## 2018 individual hospitals {.tabset}

The charts below provide the margins for each hospital grouped by region and RUCA county group. The red points are CAHs. 

Again, not a lot of conclusive evidence that CAH designation impacts financial health. If anything, these charts show that the degree at which a hospital is located in a rural area is more influential in financial health. The RUCA chart shows this by seeing that there are just larger percentages of hospitals as a whole that are reporting less than 4% margins in non-entirely urban counties.

<br>

```{r prep margins of hospitals with CAH identified in red, include = FALSE}
har.cah.margins.threshold.pr <- har.margins %>%
  mutate(threshold = ifelse(margins < .04, 1, 0)) %>%
  group_by(year, planning.region, CAH) %>%
  summarise(below.threshold = sum(threshold, na.rm = TRUE),
            total.n = n()) %>%
  ungroup() %>%
  mutate(pct.below.threshold = below.threshold / total.n)

har.cah.margins.threshold.ruca <- har.margins %>%
  mutate(threshold = ifelse(margins < .04, 1, 0)) %>%
  group_by(year, Dem_Desc, CAH) %>%
  summarise(below.threshold = sum(threshold, na.rm = TRUE),
            total.n = n()) %>%
  ungroup() %>%
  mutate(pct.below.threshold = below.threshold / total.n)


```

### Planning Region

<br>

```{r chart margins of hospitals with CAH pr}

har.margins.cah.pr.plot <- ggplot(filter(har.margins, year == 2018), aes(planning.region, margins, color = CAH)) +
    geom_point_interactive(size = 3, aes(data_id = margins, tooltip = paste(planning.region, "\nHospital Name: ", `Hospital Name`, "\nType of hospital: ", CAH, "\nTotal revenue: ", dollar(total.revenue), "\nNet income/loss: ", dollar(income.loss), "\nMargins: ", percent(margins), sep = ""))) +
    geom_label(data = filter(har.cah.margins.threshold.pr, year == 2018, CAH == "CAH"), size = 2, show.legend = FALSE, aes(x = planning.region, y = -.3, label = paste("CAH below 4%\n", below.threshold, " (", percent(pct.below.threshold), ")", sep = ""))) +
    geom_hline(yintercept = 0.04, color = "black") +
    geom_label(data = filter(har.cah.margins.threshold.pr, year == 2018, CAH == "Non-CAH"), size = 2, show.legend = FALSE, aes(x = planning.region, y = .3, label = paste("Non-CAH below 4%\n", below.threshold, " (", percent(pct.below.threshold), ")", sep = ""))) +
    labs(x="", y = "", color="", title = "Margins of each hospital - CAHs identified in red")+
    scale_y_continuous(labels=scales::percent,
                       limits = c(-.4, .4))+
    theme_line+
    scale_color_manual(values= c("red", "black"),
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = .9))
  
girafe( ggobj = har.margins.cah.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE),
                 opts_zoom(max = 3))


```

### RUCA

<br>

```{r chart margins of hospitals with CAH ruca}
har.margins.cah.ruca.plot <- ggplot(filter(har.margins, year == 2017), aes(Dem_Desc, margins, color = CAH)) +
    geom_point_interactive(size = 3, aes(data_id = margins, tooltip = paste(Dem_Desc, "\nHospital Name: ", `Hospital Name`, "\nType of hospital: ", CAH, "\nTotal revenue: ", dollar(total.revenue), "\nNet income/loss: ", dollar(income.loss), "\nMargins: ", percent(margins), sep = ""))) +
    geom_label(data = filter(har.cah.margins.threshold.ruca, year == 2017, CAH == "CAH"), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = -.3, label = paste("CAH below 4%\n", below.threshold, " (", percent(pct.below.threshold), ")", sep = ""))) +
    geom_hline(yintercept = 0.04, color = "black") +
    geom_label(data = filter(har.cah.margins.threshold.ruca, year == 2017, CAH == "Non-CAH"), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = .3, label = paste("Non-CAH below 4%\n", below.threshold, " (", percent(pct.below.threshold), ")", sep = ""))) +
    labs(x="", y = "", color="", title = "Margins of each hospital - CAHs identified in red")+
    scale_y_continuous(labels=scales::percent)+
    theme_line+
    scale_color_manual(values= c("red", "black"),
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom")

girafe( ggobj = har.margins.cah.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE),
                 opts_zoom(max = 3))

```

<br>

## Averages between CAH and non-CAH margins {.tabset}

The charts below provide the boxplots for the hospitals grouped by CAH and non-CAH in each region.

Similar to the previous charts, most of the planning regions don't experience significant differences in margins when comparing their CAH with the non-CAH. The exception is Southwest where non-CAHs have significantly lower margins than their CAHs. 

However, that changes a bit when we look at these numbers within RUCA groups. The chart shows that as a county becomes more rural, it's more likely that the non-CAHs average significantly lower margins than the CAHs. In fact, the averages are nearly twice as high in the CAHs than the non-CAHS. 
The entirely rural county group doesn't have any non-CAHs, but it's worth mentioning that the averages and medians are below the 4% threshold. 

<br>

```{r prep margins har and cah avg, include = FALSE}
har.cah.margins.avg.pr <- har.margins %>%
  group_by(year, planning.region, CAH) %>%
  summarise(mean.margins = mean(margins, na.rm = TRUE),
            median.margins = median(margins, na.rm = TRUE)) %>%
  ungroup()

har.cah.margins.avg.ruca <- har.margins %>%
  group_by(year, Dem_Desc, CAH) %>%
  summarise(mean.margins = mean(margins, na.rm = TRUE),
            median.margins = median(margins, na.rm = TRUE)) %>%
  ungroup()

```

### Planning Regions

<br>

```{r charts margins and cah boxplots pr}
har.margins.cah.box.pr.plot <- ggplot(har.margins, aes(planning.region, margins, color = CAH)) +
      geom_boxplot_interactive() +
      labs(x="", y = "", color="", title = "Boxplot of margins between CAH and regular hospitals in reach region")+
      geom_label(data = filter(har.cah.margins.avg.pr, year == 2017, CAH == "CAH"), size = 2, show.legend = FALSE, aes(x = planning.region, y = -.5, label = paste(CAH, " margins", "\nMean: ", percent(mean.margins), "\nMedian: ", percent(median.margins)))) +
      geom_label(data = filter(har.cah.margins.avg.pr, year == 2017, CAH == "Non-CAH"), size = 2, show.legend = FALSE, aes(x = planning.region, y = .5, label = paste(CAH, " margins", "\nMean: ", percent(mean.margins), "\nMedian: ", percent(median.margins)))) +
      geom_hline(yintercept = .04, color = "black") +
      scale_y_continuous(labels=scales::percent)+
      theme_line+
      scale_color_manual(values= c("red", "black"),
                         guide = guide_legend(ncol = 3)) +
      theme(legend.position = "bottom",
            axis.text.x = element_text(angle = 45, hjust = .9))
    
girafe( ggobj = har.margins.cah.box.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))    

```

### RUCA

<br>

```{r charts margins and cah boxplots ruca}
har.margins.cah.box.ruca.plot <- ggplot(har.margins, aes(Dem_Desc, margins, color = CAH)) +
      geom_boxplot_interactive() +
      labs(x="", y = "", color="", title = "Boxplot of margins between CAH and regular hospitals in reach region")+
      geom_label(data = filter(har.cah.margins.avg.ruca, year == 2017, CAH == "CAH"), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = -.5, label = paste(CAH, " margins", "\nMean: ", percent(mean.margins), "\nMedian: ", percent(median.margins)))) +
      geom_label(data = filter(har.cah.margins.avg.ruca, year == 2017, CAH == "Non-CAH"), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = .5, label = paste(CAH, " margins", "\nMean: ", percent(mean.margins), "\nMedian: ", percent(median.margins)))) +
      geom_hline(yintercept = .04, color = "black") +
      scale_y_continuous(labels=scales::percent)+
      theme_line+
      scale_color_manual(values= c("red", "black"),
                         guide = guide_legend(ncol = 3)) +
      theme(legend.position = "bottom")
    
girafe( ggobj = har.margins.cah.box.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                   opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))  
```
