---
title: "Payer mix"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
runtime: shiny
resource_files:
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.cpg
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.dbf
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.prj
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.sbn
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.sbx
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.shp.xml
- Data/Shapefiles/County shapefiles/MNCounties_MNDOT.shx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(sf)
library(ggrepel)
library(scales)
library(shiny)
library(shinycssloaders)
library(ggiraph)
library(kableExtra)
library(rmapshaper)
library(cowplot)
library(DT)
```

```{r loading jon docs and shapefiles, cache=TRUE, include=FALSE}
theme_bar <- theme_bw() +
  theme(panel.grid.major = element_line(color = "grey70", size = 0.1),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_text(face = "bold"),
        panel.border = element_blank(),
        legend.background = element_rect(fill = "transparent", color = "transparent"),
        legend.key = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

theme_line <- theme_bw() +
  theme(legend.background = element_rect(fill = "transparent", color = "transparent"),
        legend.key = element_rect(fill = "transparent"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(color = "grey70", size = 0.1),
        axis.ticks = element_blank(),
        axis.text = element_text(face = "bold"),
        panel.border = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

theme_sf <- theme_bw() +
  theme(axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "white"),
        panel.border = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.title = element_blank(),
        text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, face = "italic"),
        legend.text = element_text(margin = margin(l = 2, r = 5)))

counties.regions <- read_csv("Data/Join docs/county_regions.csv") %>%
  mutate(countyfp = formatC(countyfp, width = 3, flag = "0"),
         Name = str_to_title(Name),
         Name = str_replace(Name, "Q", "q"),
         Name = str_replace(Name, "Of The", "of the"),
         Dem_Desc = ifelse(Name == "Minnesota", "Minnesota", Dem_Desc),
         Name = str_replace(Name, "Mcleod", "McLeod"),
         planning.region = str_replace(planning.region, " Minnesota", ""),
         edr = str_replace(edr, "  ", " "))

edr.pr <- counties.regions %>%
  distinct(edr, .keep_all = TRUE) %>%
  select(5,6) %>%
  mutate(edr = str_replace(edr, "  ", " "),
         planning.region = str_replace(planning.region, " Minnesota", ""))

color.ruca <- c("Entirely rural" = "#5CA81F", "Town/rural mix" = "#C7EF99", "Urban/town/rural mix" = "#d8b365", "Entirely urban" = "#a6611a", "Minnesota" = "black")

color.pr <- c("Northwest" = "#810f7c","Northeast" = "#fe9929", "Central" = "#076324", "Seven County Mpls-St Paul" = "#d8b365", "Southwest" = "#1f78b4", "Southeast" = "#d7301f", "Minnesota" = "black")

color.edr <- c("EDR 1 - Northwest" = "#b3cde3", "EDR 2 - Headwaters" = "#8c96c6", "EDR 3 - Arrowhead" = "#fe9929", "EDR 4 - West Central" = "#8856a7", "EDR 5 - North Central" = "#810f7c", "EDR 6E- Southwest Central" = "#e5f5f9", "EDR 6W- Upper Minnesota Valley" = "#bdc9e1", "EDR 7E- East Central" = "#99d8c9", "EDR 7W- Central" = "#2ca25f", "EDR 8 - Southwest" = "#74a9cf", "EDR 9 - South Central" = "#0570b0", "EDR 10 - Southeast" = "#d7301f", "EDR 11 - 7 County Twin Cities" = "#d8b365", "Minnesota" = "black")

color.counties <- scale_color_brewer(palette = "Dark2",
                       guide = guide_legend(ncol = 3))

mn_counties <- st_read("Data/Shapefiles/county shapefiles/MNCounties_MNDOT.shp", quiet = TRUE) %>%
  ms_simplify(keep = .01, keep_shapes = TRUE)
```

```{r prep master file, include=FALSE}
master.cah.list <- read_csv("Data/HAR/CAH list.csv") %>%
  filter(STCD == "MN") %>%
  mutate(CAH = "yes",
         CITY = str_to_upper(CITY))

master.har <- read_csv("Data/HAR/Master-har.csv") %>%
  rename(year = rpt_year) %>%
  mutate(planning.region = str_replace(planning.region, " Minnesota", ""),
         edr = str_replace(edr, "  ", " ")) %>%
  left_join(master.cah.list[, c(2,11)], by = c("City" = "CITY"))

```

<br>

The charts below provides the percentage of total patient charges from all the hospitals located in each region to patients on a  public assistance program. The following programs are included;

* Medicare patient charges (code 7250)

* Medical Assistance / Prepaid Minnesota Healthcare Programs (code 7253)

* MinnesotaCare patient charges (code 7256)

These charges are summed together and is divided by the total patient charges (code 850).

It's worth noting that many of the smaller hospitals in rural areas have had specific values redacted. For example, the Tyler Hospital has values for the charges made to Medicare, PMAP, but charges to MNCare were redacted. Most of the redacted values are in hospitals that are located in rural regions where patient volumes are lowest. This likely translates that the percentages of chatges to public programs is actually higher than what is shown in the charts below.

<br>

# The percent of charges to public programs for each hospital in 2017

The table below provides the 2017 percentage of total patient charges to a public program.

<br>

```{r prep percent of charges to public program, include = FALSE}
har.ma <- master.har %>%
  filter(code %in% c(7250, 7253, 7256, 7259, 850),
         hccis_id != 145) %>%
  mutate(value = as.numeric(value),
         value = ifelse(is.na(value), 0, value),
         code = ifelse(code == 7250, "medicare",
                       ifelse(code == 7253, "ma.pmap", 
                              ifelse(code == 7256, "mncare",
                                     ifelse(code == 7259, "commercial", "total.patient.charges")))))

```

```{r percent of charges to public program table}
har.ma.table <- har.ma %>%
  group_by(year, `Hospital Name`, hccis_id, City, planning.region, Dem_Desc, CAH) %>%
  summarise(public.charges = sum(value[code %in% c("medicare", "ma.pmap", "mncare")],na.rm = TRUE),
            total.patient.charges = sum(value[code == "total.patient.charges"], na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(pct.public.charges = public.charges / total.patient.charges) %>%
  filter(year == 2017) %>%
  select(2,4,5,6,7,8,9,10)
  
  
datatable(har.ma.table, class = "cell-border stripe", filter = "top", rownames = FALSE,
          options = list(scrollX = TRUE)) %>%
    formatCurrency(6:7, "$") %>%
    formatPercentage(8)
```

<br>

# Analysis of charges to publicly insured patients by region and RUCA 

This section will examine the percent of income made in each hospital comes from public programs (Medicaid, Medicare, etc...).

<br>

## 2017 individual hospitals by region {.tabset}

The chart below provides the percentage of each hospitals charges to a patient that is publicly insured. It's obvious that hospitals in the seven-county metro have some of the lowest percentages in the state. Even more obvious is the RUCA chart which definitely shows that hospitals a concentrated around higher percentages as they become more rurally located.

<br>

```{r prep each hosptil percent public, include = FALSE}
har.ma.each <- har.ma %>%
  filter(hccis_id != 91) %>%
  group_by(year, `Hospital Name`, Dem_Desc, planning.region) %>%
  summarise(public.charges = sum(value[code %in% c("medicare", "ma.pmap", "mncare")], na.rm = TRUE),
            total.patient.charges = sum(value[code == "total.patient.charges"], na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(pct.public.charges = public.charges / total.patient.charges,
         `Hospital Name` = str_replace(`Hospital Name`, "'", "")) %>%
  mutate(Dem_Desc = fct_relevel(Dem_Desc, "Entirely rural", "Town/rural mix", "Urban/town/rural mix", "Entirely urban"),
         planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"))

```

### Planning Region

<br>

```{r chart percent public payers pr}
har.ma.each.pr.plot <- ggplot(filter(har.ma.each, year == 2017), aes(planning.region, pct.public.charges, color = planning.region)) +
    geom_point_interactive(size = 3, aes(data_id = pct.public.charges, tooltip = paste("Planning region: ", planning.region, "\nHospital name: ", `Hospital Name`, "\nPercent of patient charges to public program: ", percent(pct.public.charges)))) +
    labs(x="", y = "", color="", title = "Percent of patient charges to public program in each hospital by region")+
    scale_y_continuous(labels=scales::percent) +
    theme_line+
    scale_color_manual(values= color.pr,
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = .9))
    
girafe( ggobj = har.ma.each.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE),
                 opts_sizing(rescale = FALSE))

```

### RUCA

<br>

```{r chart percent public payers ruca}
har.ma.each.ruca.plot <- ggplot(filter(har.ma.each, year == 2017), aes(Dem_Desc, pct.public.charges, color = Dem_Desc)) +
    geom_point_interactive(size = 3, aes(data_id = pct.public.charges, tooltip = paste("RUCA County Group: ", Dem_Desc, "\nHospital name: ", `Hospital Name`, "\nPercent of patient charges to public program: ", percent(pct.public.charges)))) +
    labs(x="", y = "", color="", title = "Percent of patient charges to public program in each hospital by RUCA county group")+
    scale_y_continuous(labels=scales::percent) +
    theme_line+
    scale_color_manual(values= color.ruca,
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom")
    
girafe( ggobj = har.ma.each.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE),
                 opts_sizing(rescale = FALSE))

```

## 2017 average charges to a public program by region {.tabset}

The most interesting chart here is the RUCA. Again, rural hospitals had a significantly higher percentage of their charges going towards a public program. Our hospitals located in the state's most rural counties average nearly 70% of their charges towards a public program while our hospitals in entirely urban counties averaged 58%.

<br>

```{r prep each hospital percent public averages and medians, include = FALSE}
har.ma.avg.pr <- har.ma.each %>%
  group_by(year, planning.region) %>%
  summarise(mean.pct.public.charges = mean(pct.public.charges, na.rm = TRUE),
            median.pct.public.charges = median(pct.public.charges, na.rm = TRUE)) %>%
  ungroup()

har.ma.avg.ruca <- har.ma.each %>%
  group_by(year, Dem_Desc) %>%
  summarise(mean.pct.public.charges = mean(pct.public.charges, na.rm = TRUE),
            median.pct.public.charges = median(pct.public.charges, na.rm = TRUE)) %>%
  ungroup()
```

### Planning Region

<br>

```{r chart percent public box pr}
har.ma.box.pr.plot <- ggplot(filter(har.ma.each, year == 2017), aes(planning.region, pct.public.charges, color = planning.region)) +
    geom_boxplot_interactive() +
    geom_label(data = filter(har.ma.avg.pr, year == 2017), size = 2, show.legend = FALSE, aes(x = planning.region, y = .5, label = paste("Mean: ", percent(mean.pct.public.charges), "\nMedian: ", percent(median.pct.public.charges), sep = ""))) +
    labs(x="", y = "", color="", title = "Percent of patient charges to public program in each hospital by region")+
    scale_y_continuous(labels=scales::percent) +
    theme_line+
    scale_color_manual(values= color.pr,
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = .9))
    
girafe( ggobj = har.ma.box.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE),
                 opts_sizing(rescale = FALSE))

```

### RUCA

<br>

```{r chart percent public boxruca}
har.ma.box.ruca.plot <- ggplot(filter(har.ma.each, year == 2017), aes(Dem_Desc, pct.public.charges, color = Dem_Desc)) +
    geom_boxplot_interactive() +
    geom_label(data = filter(har.ma.avg.ruca, year == 2017), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = .5, label = paste("Mean: ", percent(mean.pct.public.charges), "\nMedian: ", percent(median.pct.public.charges), sep = ""))) +
    labs(x="", y = "", color="", title = "Percent of patient charges to public program in each hospital by RUCA county group")+
    scale_y_continuous(labels=scales::percent) +
    theme_line+
    scale_color_manual(values= color.ruca,
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom")
    
girafe( ggobj = har.ma.box.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE),
                 opts_sizing(rescale = FALSE))

```

<br>

## Trends in the percentage of patient charges to a public program {.tabset}

Are these averages a trend? According to the charts below, the averages are actually increasing across the state, but it's been typical that the twin cities metro has had some of the lowest percentages.

Per usual, the RUCA chart shows the significant diffence in the percentage of charges to a publicly insured patient. The more rural counties typically have 5 to 10 percentages points higher in their averages compared to the Entirely urban counties.

<br>

### Planning Region

<br>

```{r chart public trends pr}
har.ma.trends.pr.plot <- ggplot(har.ma.avg.pr, aes(year, mean.pct.public.charges, color = planning.region)) +
    geom_smooth(size = 2, se = FALSE) +
    geom_point_interactive(size = 3, aes(data_id = mean.pct.public.charges, tooltip = paste(planning.region, ", ", year, "\nMean percent charges to public program: ", percent(mean.pct.public.charges), sep = ""))) +
    labs(x="", y = "", color="", title = "Average charges to a public program as a percent of total charges")+
    scale_y_continuous(labels=scales::percent)+
    scale_x_continuous(breaks = seq(1900, 2050, 2)) +
    theme_line+
    scale_color_manual(values= color.pr,
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom")
  
girafe( ggobj = har.ma.trends.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))  

```

### RUCA

<br>

```{r chart public trends ruca}
har.ma.trends.ruca.plot <- ggplot(har.ma.avg.ruca, aes(year, mean.pct.public.charges, color = Dem_Desc)) +
    geom_smooth(size = 2, se = FALSE) +
    geom_point_interactive(size = 3, aes(data_id = mean.pct.public.charges, tooltip = paste(Dem_Desc, ", ", year, "\nMean percent charges to public program: ", percent(mean.pct.public.charges), sep = ""))) +
    labs(x="", y = "", color="", title = "Average charges to a public program as a percent of total charges")+
    scale_y_continuous(labels=scales::percent)+
    scale_x_continuous(breaks = seq(1900, 2050, 2)) +
    theme_line+
    scale_color_manual(values= color.ruca,
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom")

girafe( ggobj = har.ma.trends.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))  

```




<br>

# Analysis of charges to publicly insured patients by CAH and non-CAH {.tabset}

The charts below provide the percentage of total patient charges that go towards a public program with CAHs designated by red dots. The averages for each type of hospital are provided in the text boxes.

As can be seen, there isn't a ton of difference in percentages between CAH and non-CAHs in each of the regions. The Southern half of the state sees the most significant difference.

<br>

```{r prep pct charges to public programs CAH vs Non-CAH, include = FALSE}
har.cah.ma.each <- har.ma %>%
  group_by(year, `Hospital Name`, CAH, Dem_Desc, planning.region) %>%
  summarise(public.charges = sum(value[code %in% c("medicare", "ma.pmap", "mncare")], na.rm = TRUE),
            total.charges = sum(value[code == "total.patient.charges"], na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(pct.public.charges = public.charges / total.charges,
         CAH = ifelse(is.na(CAH), "non-CAH", "CAH"),
         `Hospital Name` = str_replace(`Hospital Name`, "'", ""),
         Dem_Desc = fct_relevel(Dem_Desc, "Entirely rural", "Town/rural mix", "Urban/town/rural mix", "Entirely urban"),
         planning.region = fct_relevel(planning.region, "Northwest", "Northeast", "Central", "Seven County Mpls-St Paul", "Southwest", "Southeast"))

har.cah.ma.avg.pr <- har.cah.ma.each %>%
  group_by(year, planning.region, CAH) %>%
  summarise(mean.pct.public.charges = mean(pct.public.charges, na.rm = TRUE),
            median.pct.public.charges = median(pct.public.charges,na.rm = TRUE)) %>%
  ungroup()

har.cah.ma.avg.ruca <- har.cah.ma.each %>%
  group_by(year, Dem_Desc, CAH) %>%
  summarise(mean.pct.public.charges = mean(pct.public.charges, na.rm = TRUE),
            median.pct.public.charges = median(pct.public.charges,na.rm = TRUE)) %>%
  ungroup()

```

## Planning Regions

<br>

```{r charts pct charges to public CAH pr}
har.cah.ma.each.pr.plot <- ggplot(data = filter(har.cah.ma.each, year == 2017), aes(planning.region, pct.public.charges, color = CAH)) +
    geom_point_interactive(size = 3, aes(data_id = pct.public.charges, tooltip = paste(planning.region, "\n", `Hospital Name`, "\nHospital type: ", CAH, "\nTotal patient charges: ", dollar(total.charges), "\nCharges to public program: ", dollar(public.charges), "\nPercent of charges to public program: ", percent(pct.public.charges), sep = ""))) +
    geom_label(data = filter(har.cah.ma.avg.pr, year == 2017, CAH == "CAH"), size = 2, show.legend = FALSE, aes(x = planning.region, y = .5, label = paste(CAH, "\nMean: ", percent(mean.pct.public.charges), "\nMedian: ", percent(median.pct.public.charges), sep = ""))) +
    geom_label(data = filter(har.cah.ma.avg.pr, year == 2017, CAH == "non-CAH"), size = 2, show.legend = FALSE, aes(x = planning.region, y = .9, label = paste(CAH, "\nMean: ", percent(mean.pct.public.charges), "\nMedian: ", percent(median.pct.public.charges), sep = ""))) +
    labs(x="", y = "", color="", title = "Percent of charges to a public program with CAH designation in red")+
    scale_y_continuous(labels=scales::percent,
                       limits = c(.4, 1))+
    theme_line+
    scale_color_manual(values= c("red", "black"),
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = .9))
  
girafe( ggobj = har.cah.ma.each.pr.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))

```

## RUCA

<br>

```{r charts pct charges to public CAH ruca}
har.cah.ma.each.ruca.plot <- ggplot(data = filter(har.cah.ma.each, year == 2017), aes(Dem_Desc, pct.public.charges, color = CAH)) +
    geom_point_interactive(size = 3, aes(data_id = pct.public.charges, tooltip = paste(Dem_Desc, "\n", `Hospital Name`, "\nHospital type: ", CAH,  "\nTotal patient charges: ", dollar(total.charges), "\nCharges to public program: ", dollar(public.charges), "\nPercent of charges to public program: ", percent(pct.public.charges), sep = ""))) +
    geom_label(data = filter(har.cah.ma.avg.ruca, year == 2017, CAH == "CAH"), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = .5, label = paste(CAH, "\nMean: ", percent(mean.pct.public.charges), "\nMedian: ", percent(median.pct.public.charges), sep = ""))) +
    geom_label(data = filter(har.cah.ma.avg.ruca, year == 2017, CAH == "non-CAH"), size = 2, show.legend = FALSE, aes(x = Dem_Desc, y = .9, label = paste(CAH, "\nMean: ", percent(mean.pct.public.charges), "\nMedian: ", percent(median.pct.public.charges), sep = ""))) +
    labs(x="", y = "", color="", title = "Percent of charges to a public program with CAH designation in red")+
    scale_y_continuous(labels=scales::percent,
                       limits = c(.4, 1))+
    theme_line+
    scale_color_manual(values= c("red", "black"),
                       guide = guide_legend(ncol = 3)) +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = .9))
  
girafe( ggobj = har.cah.ma.each.ruca.plot, width_svg = 8) %>%
  girafe_options(opts_selection(type = "none"),
                 opts_toolbar(saveaspng = FALSE) ,
                 opts_sizing(rescale = FALSE))

```
